On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Cosmetics

\begin{dfn}
	The diameter of the integral point set $\mathcal{P}$ is defined as
	\begin{equation}
		\operatorname{diam(\mathcal{P})} = \underset{P_{1}, P_{2} \in
		\mathcal{P}}{\max} |P_{1}P_{2}|
	\end{equation}
\end{dfn}

@@

\begin{dfn}
	A planar integral point sets of $n$ points with $n-1$ points on a straight line is called
	a \textit{facher} set.
\end{dfn}
Facher sets are very dominating examples of planar integral pont sets.
In~\cite{antonov2008maximal}, facher sets of characteristic 1 are called \textit{semi-crabs}.
For $9 \leq n \leq 122$, the diameter $d(2,n)$ is reached on a facher point set~\cite{kurz2008minimum}.

@@

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/42_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 42 and diameter 2473117504}
\label{42_symm.png}}
\end{figure}

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/46_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 46 and diameter 3118278592}
\label{46_symm.png}}
\end{figure}

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/48_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 48 and diameter 71720407616}
\label{48_symm.png}}
\end{figure}

@@

\item
$\mathcal{P_42}=\sqrt{154}/{1} * \{
(\pm 345596160; 0);
(\pm219513840 -15069600);
(\pm260201760; 0);\\
(\pm225792840; 0);
(\pm213234840; 0);
(\pm153961080; 0);
(\pm144668160; 0);
(\pm25116000; 0);\\
(\pm694026840; 0);
(\pm514710560; 0);
(\pm359116940; 0);
(\pm13423904; 0);
(\pm75682880; 0);\\
(\pm464143680; 0);
(\pm827069880; 0);
(\pm92144325; 0);
(\pm1195180740; 0);
(\pm1236558752; 0);\\
(\pm44590560; 0);
(\pm339925740; 0);
(\pm117312468; 0)\}
$
(Figure~\ref{42_symm.png}),

where $n = 42$, $\operatorname{diam(\mathcal{P})} = 2473117504$.

\item
$\mathcal{P_46}=\sqrt{154}/{1} * \{
(\pm435751680; 0);
(\pm276778320; -19000800);
(\pm328080480; 0);
(\pm284695320; 0);\\
(\pm268861320; 0);
(\pm194124840; 0);
(\pm182407680; 0);
(\pm31668000; 0);
(\pm1559139296; 0);\\
(\pm1506967020; 0);
(\pm1042827240; 0);
(\pm875077320; 0);
(\pm648982880; 0);
(\pm585224640; 0);\\
(\pm452799620; 0);
(\pm95426240; 0);
(\pm16925792; 0);
(\pm116181975; 0);
(\pm428602020; 0);\\
(\pm56222880; 0);
(\pm769560480; 0);
(\pm626458560; 0);
(\pm130761918; 0)\}
$
(Figure~\ref{46_symm.png}),

where $n = 46$, $\operatorname{diam(\mathcal{P})} = 3118278592$.

\item
$\mathcal{P_48}=\sqrt{154}/{1} * \{
( \pm10022288640; 0);
( \pm6365901360 ; -437018400);
( \pm7545851040 ; 0);\\
( \pm6547992360 ; 0);
( \pm6183810360 ; 0);
( \pm4464871320 ; 0);
( \pm4195376640 ; 0);
( \pm728364000 ; 0);\\
( \pm35860203808 ; 0);
( \pm34660241460 ; 0);
( \pm23985026520 ; 0);
( \pm20126778360 ; 0);\\
( \pm14926606240 ; 0);
( \pm13460166720 ; 0);
( \pm10414391260 ; 0);
( \pm2194803520 ; 0);
( \pm389293216 ; 0);\\
( \pm2672185425 ; 0);
( \pm9857846460 ; 0);
( \pm1293126240 ; 0);
( \pm17699891040 ; 0);
( \pm14408546880 ; 0);\\
( \pm3007524114 ; 0);
( \pm3402061572 ; 0)\}
$
(Figure~\ref{48_symm.png}),

@@

Taking the examples into consideration,
we can conjecture that there is an infinite set with rational distances
that contains $\mathcal{P_48}$.
(However, it is known~\cite{solymosi2010question} that
if a rational set $S$ has infinitely many points on a line or on a circle,
then all but 4 resp. 3 points of $S$ are on the line or on the circle.)

@@

@@

Note that distance between the non-adoptable points is
\begin{equation}
	\sqrt{\left(\frac{1767}{2} - \frac{340}{2}\right)^2 + \left(\frac{147}{2}\right)^2\cdot143} = 2\sqrt{320401}
	.
\end{equation}
It's notable that 320401 is a prime number.

@@

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/15_61960444_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 15 and diameter 61960444}
\label{15_61960444_1.png}}
\end{figure}

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/15_45970652_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 15 and diameter 45970652}
\label{15_45970652_1.png}}
\end{figure}

>>>>

\begin{dfn}
	The diameter of the integral point set $\mathcal{P}$ is defined as
	\begin{equation}
		\operatorname{diam(\mathcal{P})} = \underset{P_{1}, P_{2} \in
		\mathcal{P}}{\max} |P_{1}P_{2}|
		.
	\end{equation}
\end{dfn}

@@

\begin{dfn}
	A planar integral point sets of $n$ points with $n-1$ points on a straight line is called
	a \textit{facher} set.
\end{dfn}
Facher sets are very dominating examples of planar integral pont sets.
In~\cite{antonov2008maximal}, facher sets of characteristic 1 are called \textit{semi-crabs}.
%For $9 \leq n \leq 122$, the diameter $d(2,n)$ is reached on a facher point set~\cite{kurz2008minimum}.

@@

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/42_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 42 and diameter 2473117504}
\label{42_symm.png}}
\end{figure}

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/46_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 46 and diameter 3118278592}
\label{46_symm.png}}
\end{figure}

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/48_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 48 and diameter 71720407616}
\label{48_symm.png}}
\end{figure}

@@

\item
Figure~\ref{42_symm.png}:
\\
$\mathcal{P}_{42}=\sqrt{154}/{1} * \{
(\pm 345596160; 0);
(\pm219513840; -15069600);
(\pm260201760; 0);\\
(\pm225792840; 0);
(\pm213234840; 0);
(\pm153961080; 0);
(\pm144668160; 0);
(\pm25116000; 0);\\
(\pm694026840; 0);
(\pm514710560; 0);
(\pm359116940; 0);
(\pm13423904; 0);
(\pm75682880; 0);\\
(\pm464143680; 0);
(\pm827069880; 0);
(\pm92144325; 0);
(\pm1195180740; 0);
(\pm1236558752; 0);\\
(\pm44590560; 0);
(\pm339925740; 0);
(\pm117312468; 0)\}
$

\item
Figure~\ref{46_symm.png}:
\\
$\mathcal{P}_{46}=\sqrt{154}/{1} * \{
(\pm435751680; 0);
(\pm276778320; -19000800);
(\pm328080480; 0);
(\pm284695320; 0);\\
(\pm268861320; 0);
(\pm194124840; 0);
(\pm182407680; 0);
(\pm31668000; 0);
(\pm1559139296; 0);\\
(\pm1506967020; 0);
(\pm1042827240; 0);
(\pm875077320; 0);
(\pm648982880; 0);
(\pm585224640; 0);\\
(\pm452799620; 0);
(\pm95426240; 0);
(\pm16925792; 0);
(\pm116181975; 0);
(\pm428602020; 0);\\
(\pm56222880; 0);
(\pm769560480; 0);
(\pm626458560; 0);
(\pm130761918; 0)\}
$

\item
Figure~\ref{48_symm.png}:
\\
$\mathcal{P}_{48}=\sqrt{154}/{1} * \{
( \pm10022288640; 0);
( \pm6365901360 ; -437018400);
( \pm7545851040 ; 0);\\
( \pm6547992360 ; 0);
( \pm6183810360 ; 0);
( \pm4464871320 ; 0);
( \pm4195376640 ; 0);
( \pm728364000 ; 0);\\
( \pm35860203808 ; 0);
( \pm34660241460 ; 0);
( \pm23985026520 ; 0);
( \pm20126778360 ; 0);\\
( \pm14926606240 ; 0);
( \pm13460166720 ; 0);
( \pm10414391260 ; 0);
( \pm2194803520 ; 0);
( \pm389293216 ; 0);\\
( \pm2672185425 ; 0);
( \pm9857846460 ; 0);
( \pm1293126240 ; 0);
( \pm17699891040 ; 0);
( \pm14408546880 ; 0);\\
( \pm3007524114 ; 0);
( \pm3402061572 ; 0)\}
$

@@

Taking the examples into consideration,
we can conjecture that there is an infinite point set with rational distances
that contains $\mathcal{P}_{48}$.
(However, it is known~\cite{solymosi2010question} that
if a point set $S$ with rational distances has infinitely many points on a line or on a circle,
then all but 4 resp. 3 points of $S$ are on the line or on the circle.)

@@

Figure~\ref{8_with_many_common} shows an example of three PIPS of cardinality 8,
each pair of that shares 6 or 7 points but cannot be united into another PIPS.

@@

The distance between the non-adoptable points is
\begin{equation}
	\sqrt{\left(\frac{1767}{2} - \frac{340}{2}\right)^2 + \left(\frac{147}{2}\right)^2\cdot143} = 2\sqrt{320401}
	.
\end{equation}
It's notable that 320401 is a prime number.

@@

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/15_61960444_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 15 and diameter 61960444}
\label{15_61960444_1.png}}
\end{figure}

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/15_45970652_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 15 and diameter 45970652}
\label{15_45970652_1.png}}
\end{figure}
